\Title

### 2020-04-07 manuscript/manuscript.tex
Remove pad rows on parameter tables
Started reviewing the introduction
Got through the first two paragraphs. Minor re-wording and added a
reference to the method in GMT's `surface` module.

Potential field data, like gravity and magnetics, are useful for geophysics
exploration.
The potential field data can be obtained from ground, airborne or satellite
measurements.
On ground surveys the data is often gathered on scattered points or following
irregular paths, usually at the topographic surface.
The data points have different heights.
On airborne surveys the data is gathered on flight paths, producing a large
number of data points concentrated along almost straight lines.
The height of measurement could change because of the vertical movement of the
airship.
To improve visualization of the data for interpretation and to prepare the data
for processing through different methods (RTP, upward continuation, Euler
deconvolution, etc), the data needs to be interpolated on a regular grid of
data points.

There are several methods for interpolating 2D data like minimum curvature,
biharmonic Splines or Kriging.
These all-purpose methods show a few problems when applied to potential field
data.
(i) They don't take into account the height of the observation points.
Potential field data has a strong dependency on measurement height.
(ii) The predicted grid data is not necessary an Harmonic function.
(iii) They don't usually take into account the anisotropy of the observation
points in ground and airborne surveys.

>>>>

Measurements of anomalies in potential fields, like gravity disturbances and
total-field magnetic anomalies, are widely used in geophysical exploration for
their relatively low cost of acquisition.
These data can be surveyed using ground, airborne, shipborne, or satellite
systems.
In ground surveys, the data are often gathered following
irregular paths or networks along the surface of the terrain, leading to highly
variable elevations in mountainous regions.
On airborne surveys, the data are gathered along flight lines, producing a
large number of measurements concentrated along almost straight lines.
In surveys that drape the topography, the height of measurement could change
dramatically because of the vertical movement of the aircraft.
Processing of the data often involves interpolation onto a regular grid at
constant height, both to improve visualization for interpretation purposes as
well as to prepare the data for further processing and modelling (e.g.,
reduction-to-the-pole, derivative calculations, upward continuation, Euler
deconvolution),

Several methods exist in the literature for interpolation in two dimensions,
for example continuous curvature splines in tension \citep{smith1990},
biharmonic (thin-plate) splines \citep{sandwell1987}, and kriging.
These general-purpose methods have limitations when it comes to interpolating
potential field data:
(i) they are not able to take into account the variable height of the
observation points;
(ii) the interpolating functions are not necessarily harmonic functions, which
is the underlying assumption behind many processing techniques
(e.g., upward continuation and vertical derivatives).
